---
title: "Pre-book Airport Parking Performance Analysis"
author: "Myrvens Sylvestre"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: hide
    theme: cosmo
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE, 
  message = FALSE,
  fig.width = 12, 
  fig.height = 7,
  fig.align = "center"
)

.libPaths(c("C:/Temp/R_packages", .libPaths()))
setwd("C:/Users/Myrvens Sylvestre/Downloads/Capstone")
```

```{r load-libraries, include=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(tidyverse)
library(lubridate)
library(scales)
library(knitr)
library(kableExtra)
library(ragg)

cat("✓ All packages loaded successfully\n")
```

```{r load-data, include=FALSE}
data <- readRDS("prebook_parking_3months_CLEANED.rds")

data_clean <- data %>%
  filter(!is.na(car_park_name) & car_park_name != "MISSING TRANSLATION")

cat("✓ Clean dataset created\n")
cat("  Original rows:", nrow(data), "\n")
cat("  Clean rows:", nrow(data_clean), "\n")
cat("  Rows removed (MISSING TRANSLATION):", nrow(data) - nrow(data_clean), "\n")
```

```{r shared-theme, include=FALSE}
chart_theme <- theme_minimal(base_size = 13) +
  theme(
    plot.title         = element_text(size = 18, color = "#000000", family = "sans"),  # Changed from 14 to 18
    plot.subtitle      = element_blank(),
    plot.caption       = element_blank(),
    axis.text.x        = element_text(color = "#000000", size = 11, family = "sans"),
    axis.text.y        = element_text(color = "#000000", size = 11, family = "sans"),
    axis.text.y.right  = element_text(color = "#000000", size = 11, family = "sans"),
    axis.title.x       = element_text(color = "#000000", size = 12, family = "sans"),
    axis.title.y       = element_text(color = "#000000", size = 12, family = "sans"),
    axis.title.y.right = element_text(color = "#000000", size = 12, family = "sans"),
    legend.position    = "top",
    legend.text        = element_text(size = 11, family = "sans"),
    legend.title       = element_blank(),
    panel.grid.major   = element_line(color = "#E0E0E0"),
    panel.grid.minor   = element_blank(),
    strip.background   = element_rect(fill = "#E8F4F8", color = NA),
    strip.text         = element_text(size = 11, color = "#000000", family = "sans")
  )
```

---

# Executive Summary

```{r executive-summary}
total_bookings    <- nrow(data_clean)
total_revenue     <- sum(data_clean$booking_current_value, na.rm = TRUE)
total_cancelled   <- sum(data_clean$is_cancelled, na.rm = TRUE)
cancellation_rate <- mean(data_clean$is_cancelled, na.rm = TRUE) * 100
avg_duration      <- mean(data_clean$duration, na.rm = TRUE)
date_range_start  <- min(data_clean$booking_date, na.rm = TRUE)
date_range_end    <- max(data_clean$booking_date, na.rm = TRUE)

lot_performance <- data_clean %>%
  group_by(car_park_name) %>%
  summarise(
    total_revenue = sum(booking_current_value, na.rm = TRUE),
    bookings = n(),
    .groups = "drop"
  ) %>%
  arrange(desc(total_revenue))

top_lot         <- lot_performance$car_park_name[1]
top_lot_revenue <- lot_performance$total_revenue[1]
```

:::{.alert .alert-info}
**Analysis Period:** `r format(date_range_start, "%B %d, %Y")` to `r format(date_range_end, "%B %d, %Y")`

**Dataset Overview:**

- **Total Bookings:** `r format(total_bookings, big.mark = ",")`
- **Total Revenue:** `r dollar(total_revenue)`
- **Cancellation Rate:** `r round(cancellation_rate, 2)`%
- **Average Stay Duration:** `r round(avg_duration, 1)` days
- **Top Performing Lot:** **`r top_lot`** (`r dollar(top_lot_revenue)`)
:::

---

# 1. Parking Lot Overview

## 1.1 Quick Stats by Lot

```{r lot-overview-table}
lot_overview <- data_clean %>%
  group_by(car_park_name) %>%
  summarise(
    Bookings              = n(),
    `Total Revenue`       = sum(booking_current_value, na.rm = TRUE),
    `Avg Revenue/Booking` = mean(booking_current_value, na.rm = TRUE),
    `Avg Duration (days)` = mean(duration, na.rm = TRUE),
    `Cancellations`       = sum(is_cancelled, na.rm = TRUE),
    `Cancel Rate (%)`     = mean(is_cancelled, na.rm = TRUE) * 100,
    .groups = "drop"
  ) %>%
  arrange(desc(`Total Revenue`))

kable(lot_overview,
      digits = 2,
      format.args = list(big.mark = ","),
      caption = "Parking Lot Performance Snapshot") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, color = "#1F4E78") %>%
  row_spec(1, bold = TRUE, background = "#D5E8D4")
```

## 1.2 Visual Comparison

```{r lot-overview-chart, fig.height=6}
ggplot(lot_overview, aes(x = reorder(car_park_name, -`Total Revenue`),
                         y = Bookings,
                         fill = car_park_name)) +
  geom_col(alpha = 0.85, width = 0.7) +
  geom_text(aes(label = paste0(format(Bookings, big.mark = ","), "\n",
                                dollar(`Total Revenue`))),
            vjust = -0.5, size = 3.5, color = "#000000", family = "sans") +
  scale_fill_brewer(palette = "Set3") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
  labs(
    title = "Bookings and Revenue - By Parking Lot",
    x     = "Parking Lot",
    y     = "Number of Bookings"
  ) +
  chart_theme +
  theme(
    legend.position    = "none",
    panel.grid.major.x = element_blank()
  )

ggsave("visualizations/lot_overview.png", width = 12, height = 6,
       dpi = 300, bg = "white", device = ragg::agg_png)
```

---

# 2. Revenue Story: Which Lots Make the Most Money?

## 2.1 Total Revenue Comparison

```{r revenue-by-lot, fig.height=7}
ggplot(lot_overview, aes(x = reorder(car_park_name, `Total Revenue`),
                         y = `Total Revenue`,
                         fill = car_park_name)) +
  geom_col(alpha = 0.85, width = 0.7) +
  geom_text(aes(label = paste0(dollar(`Total Revenue`), "\n(",
                                format(Bookings, big.mark = ","), " bookings)")),
            hjust = -0.1, size = 3.5, color = "#000000", family = "sans") +
  scale_fill_brewer(palette = "Set2") +
  scale_y_continuous(labels = dollar_format(),
                     expand = expansion(mult = c(0, 0.2))) +
  coord_flip() +
  labs(
    title = "Total Revenue - By Parking Lot",
    x     = "Parking Lot",
    y     = "Total Revenue"
  ) +
  chart_theme +
  theme(legend.position = "none")

ggsave("visualizations/revenue_by_lot_total.png", width = 12, height = 7,
       dpi = 300, bg = "white", device = ragg::agg_png)
```

:::{.alert .alert-success}
**Key Finding:** `r top_lot` generates the most revenue at `r dollar(top_lot_revenue)`, representing `r round(top_lot_revenue/total_revenue * 100, 1)`% of total revenue with `r format(lot_performance$bookings[1], big.mark = ",")` bookings.
:::

## 2.2 Revenue Efficiency: Revenue per Day

```{r revenue-efficiency-by-lot}
revenue_efficiency <- data_clean %>%
  filter(!is.na(duration) & duration > 0) %>%
  mutate(revenue_per_day = booking_current_value / duration) %>%
  group_by(car_park_name) %>%
  summarise(
    bookings                = n(),
    avg_revenue_per_day     = mean(revenue_per_day, na.rm = TRUE),
    avg_revenue_per_booking = mean(booking_current_value, na.rm = TRUE),
    avg_duration            = mean(duration, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(desc(avg_revenue_per_day))

kable(revenue_efficiency,
      digits = 2,
      col.names = c("Parking Lot", "Bookings", "Avg $/Day",
                    "Avg $/Booking", "Avg Duration (days)"),
      caption = "Revenue Efficiency Metrics by Lot") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(3, background = "#FFF3CD")
```

```{r revenue-efficiency-chart}
ggplot(revenue_efficiency, aes(x = reorder(car_park_name, avg_revenue_per_day),
                               y = avg_revenue_per_day,
                               fill = car_park_name)) +
  geom_col(alpha = 0.85, width = 0.7) +
  geom_text(aes(label = sprintf("$%.2f/day\n(%d bookings)",
                                avg_revenue_per_day, bookings)),
            hjust = -0.1, size = 3.5, color = "#000000", family = "sans") +
  geom_hline(yintercept = mean(revenue_efficiency$avg_revenue_per_day),
             linetype = "dashed", color = "#C0504D", linewidth = 1) +
  scale_fill_brewer(palette = "Pastel1") +
  scale_y_continuous(labels = dollar_format(),
                     expand = expansion(mult = c(0, 0.2))) +
  coord_flip() +
  labs(
    title = "Revenue per Day - By Parking Lot",
    x     = "Parking Lot",
    y     = "Average Revenue per Day"
  ) +
  chart_theme +
  theme(legend.position = "none")

ggsave("visualizations/revenue_efficiency_by_lot.png", width = 12, height = 7,
       dpi = 300, bg = "white", device = ragg::agg_png)
```

## 2.3 Revenue vs Arrivals by Hour

```{r revenue-vs-arrivals-by-hour, fig.height=7}
revenue_arrivals_by_hour <- data_clean %>%
  mutate(
    booking_hour = hour(booking_date),
    booking_day  = as.Date(booking_date)
  ) %>%
  group_by(booking_day, booking_hour) %>%
  summarise(
    daily_bookings    = n(),
    daily_avg_revenue = mean(booking_current_value, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  group_by(booking_hour) %>%
  summarise(
    avg_arrivals = mean(daily_bookings),
    avg_revenue  = mean(daily_avg_revenue),
    .groups = "drop"
  )

scale_factor <- max(revenue_arrivals_by_hour$avg_revenue,  na.rm = TRUE) /
                max(revenue_arrivals_by_hour$avg_arrivals, na.rm = TRUE)

ggplot(revenue_arrivals_by_hour, aes(x = booking_hour)) +
  geom_line(aes(y = avg_revenue,                color = "Average Revenue"),  linewidth = 1.2) +
  geom_line(aes(y = avg_arrivals * scale_factor, color = "Average Arrivals"), linewidth = 1.2) +
  scale_color_manual(
    values = c("Average Revenue"  = "#4472C4",
               "Average Arrivals" = "#C0504D"),
    breaks = c("Average Arrivals", "Average Revenue")
  ) +
  scale_y_continuous(
    labels   = dollar_format(),
    name     = "Average Revenue",
    sec.axis = sec_axis(transform = ~ . / scale_factor,
                        name      = "Average Arrivals")
  ) +
  scale_x_continuous(breaks = seq(0, 23, 5)) +
  labs(
    title = "Revenue vs Arrivals - By Hour of Day",
    x     = "Hour of Day",
    color = NULL
  ) +
  chart_theme

ggsave("visualizations/revenue_vs_arrivals_by_hour.png", width = 12, height = 7,
       dpi = 300, bg = "white", device = ragg::agg_png)
```

---

# 3. Customer Behavior: How Do Parking Patterns Differ?

## 3.1 Duration Patterns by Lot

```{r duration-by-lot}
duration_by_lot <- data_clean %>%
  filter(!is.na(duration) & duration > 0) %>%
  group_by(car_park_name) %>%
  summarise(
    bookings        = n(),
    avg_duration    = mean(duration, na.rm = TRUE),
    median_duration = median(duration, na.rm = TRUE),
    min_duration    = min(duration, na.rm = TRUE),
    max_duration    = max(duration, na.rm = TRUE),
    short_stay      = sum(duration <= 3),
    medium_stay     = sum(duration > 3 & duration <= 7),
    long_stay       = sum(duration > 7),
    .groups = "drop"
  ) %>%
  arrange(desc(avg_duration))

kable(duration_by_lot,
      digits = 2,
      col.names = c("Lot", "Bookings", "Avg", "Median", "Min", "Max",
                    "≤3 days", "4-7 days", "8+ days"),
      caption = "Parking Duration Statistics by Lot") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
  add_header_above(c(" " = 2, "Duration (days)" = 4, "Stay Categories" = 3)) %>%
  column_spec(1, bold = TRUE)
```

```{r duration-comparison-chart}
ggplot(duration_by_lot, aes(x = reorder(car_park_name, avg_duration),
                            y = avg_duration,
                            fill = car_park_name)) +
  geom_col(alpha = 0.85, width = 0.7) +
  geom_text(aes(label = sprintf("%.1f days\n(%d bookings)", avg_duration, bookings)),
            vjust = -0.5, size = 3.5, color = "#000000", family = "sans") +
  geom_hline(yintercept = mean(data_clean$duration, na.rm = TRUE),
             linetype = "dashed", color = "#808080", linewidth = 1) +
  scale_fill_brewer(palette = "Set3") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
  labs(
    title = "Average Parking Duration - By Lot",
    x     = "Parking Lot",
    y     = "Average Duration (days)"
  ) +
  chart_theme +
  theme(
    legend.position    = "none",
    panel.grid.major.x = element_blank()
  )

ggsave("visualizations/duration_by_lot.png", width = 12, height = 7,
       dpi = 300, bg = "white", device = ragg::agg_png)
```

## 3.2 Stay Duration Distribution by Lot

```{r duration-distribution-lot, fig.height=8}
duration_categories <- data_clean %>%
  filter(!is.na(duration) & duration > 0) %>%
  mutate(
    category = case_when(
      duration <= 3 ~ "Short Stay (1-3 days)",
      duration <= 7 ~ "Medium Stay (4-7 days)",
      TRUE          ~ "Long Stay (8+ days)"
    ),
    category = factor(category,
                      levels = c("Short Stay (1-3 days)",
                                 "Medium Stay (4-7 days)",
                                 "Long Stay (8+ days)"))
  ) %>%
  group_by(car_park_name, category) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(car_park_name) %>%
  mutate(percentage = count / sum(count) * 100)

ggplot(duration_categories, aes(x = car_park_name, y = percentage, fill = category)) +
  geom_col(alpha = 0.85, width = 0.7, position = "stack") +
  geom_text(aes(label = sprintf("%.0f%%", percentage)),
            position = position_stack(vjust = 0.5),
            size = 3.5, color = "white", family = "sans") +
  scale_fill_manual(values = c("#A8D5BA", "#F4A460", "#C5A3D0")) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Stay Duration Distribution - By Parking Lot",
    x     = "Parking Lot",
    y     = "Percentage of Bookings (%)",
    fill  = "Stay Category"
  ) +
  chart_theme +
  theme(
    legend.position    = "top",
    panel.grid.major.x = element_blank()
  )

ggsave("visualizations/duration_distribution_by_lot.png", width = 12, height = 8,
       dpi = 300, bg = "white", device = ragg::agg_png)
```

## 3.3 Peak Arrival Days by Lot

```{r arrival-day-by-lot, fig.height=10}
arrival_by_lot <- data_clean %>%
  filter(!is.na(booking_arrival_date)) %>%
  mutate(
    arrival_dow = wday(booking_arrival_date, label = TRUE, abbr = FALSE),
    arrival_dow = factor(arrival_dow,
                         levels = c("Monday", "Tuesday", "Wednesday", "Thursday",
                                    "Friday", "Saturday", "Sunday"))
  ) %>%
  group_by(car_park_name, arrival_dow) %>%
  summarise(bookings = n(), .groups = "drop")

ggplot(arrival_by_lot, aes(x = arrival_dow, y = bookings, fill = arrival_dow)) +
  geom_col(alpha = 0.85, width = 0.7) +
  geom_text(aes(label = bookings), vjust = -0.5, size = 3,
            color = "#000000", family = "sans") +
  facet_wrap(~ car_park_name, ncol = 2, scales = "free_y") +
  scale_fill_brewer(palette = "Pastel1") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
  labs(
    title = "Customer Arrival Patterns - By Day of Week",
    x     = "Day of Week",
    y     = "Number of Bookings"
  ) +
  chart_theme +
  theme(
    legend.position = "none",
    axis.text.x     = element_text(color = "#000000", size = 10,
                                   angle = 45, hjust = 1, family = "sans")
  )

ggsave("visualizations/arrival_day_by_lot.png", width = 12, height = 10,
       dpi = 300, bg = "white", device = ragg::agg_png)
```

---

# 4. Cancellation Story: Which Lots Have Problems?

## 4.1 Cancellation Rate by Day of Week

```{r cancellation-rate-dow, fig.height=6}
cancellation_by_dow <- data_clean %>%
  mutate(
    booking_dow = wday(booking_date, label = TRUE, abbr = FALSE),
    booking_dow = factor(booking_dow,
                         levels = c("Monday", "Tuesday", "Wednesday", "Thursday",
                                    "Friday", "Saturday", "Sunday"))
  ) %>%
  group_by(booking_dow) %>%
  summarise(
    total_bookings = n(),
    cancellations  = sum(is_cancelled, na.rm = TRUE),
    cancel_rate    = mean(is_cancelled, na.rm = TRUE) * 100,
    .groups = "drop"
  )

overall_avg <- mean(data_clean$is_cancelled, na.rm = TRUE) * 100

ggplot(cancellation_by_dow, aes(x = booking_dow, y = cancel_rate, fill = booking_dow)) +
  geom_col(alpha = 0.85, width = 0.7) +
  geom_text(aes(label = sprintf("%.1f%%", cancel_rate)),
            vjust = -0.8, size = 4, color = "#000000", family = "sans") +
  geom_text(aes(label = sprintf("(%d/%d)", cancellations, total_bookings)),
            vjust = -2.4, size = 3.5, color = "#000000", family = "sans") +
  geom_hline(yintercept = overall_avg,
             linetype = "dashed", color = "#C0504D", linewidth = 1) +
  scale_fill_hue() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.25))) +
  labs(
    title = "Cancellation Rate - By Day of Week",
    x     = "Day of Week",
    y     = "Cancellation Rate (%)"
  ) +
  chart_theme +
  theme(
    legend.position    = "none",
    panel.grid.major.x = element_blank()
  )

ggsave("visualizations/cancellation_rate_by_day.png", width = 12, height = 6,
       dpi = 300, bg = "white", device = ragg::agg_png)
```

## 4.2 Cancellation Rate by Lot

```{r cancellation-rate-by-lot}
cancellation_by_lot <- data_clean %>%
  group_by(car_park_name) %>%
  summarise(
    total_bookings = n(),
    cancellations  = sum(is_cancelled, na.rm = TRUE),
    active         = sum(!is_cancelled, na.rm = TRUE),
    cancel_rate    = mean(is_cancelled, na.rm = TRUE) * 100,
    .groups = "drop"
  ) %>%
  arrange(desc(cancel_rate))

kable(cancellation_by_lot,
      digits = 2,
      col.names = c("Lot", "Total Bookings", "Cancelled", "Active", "Cancel Rate (%)"),
      caption = "Cancellation Statistics by Parking Lot") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(5, background = "#FFE6E6")
```

```{r cancellation-rate-chart}
# Fix: force lots into numeric order (2, 3, 4, 5, 6)
cancellation_by_lot$car_park_name <- factor(
  cancellation_by_lot$car_park_name,
  levels = c("Lot 2 General", "Lot 3", "Lot 4 General", "Lot 5", "Lot 6")
)

ggplot(cancellation_by_lot, aes(x = car_park_name,
                                y = cancel_rate,
                                fill = car_park_name)) +
  geom_col(alpha = 0.85, width = 0.7) +
  geom_text(aes(label = sprintf("%.1f%%\n(%d/%d)",
                                cancel_rate, cancellations, total_bookings)),
            vjust = -0.5, size = 3.5, color = "#000000", family = "sans") +
  geom_hline(yintercept = cancellation_rate,
             linetype = "dashed", color = "#C0504D", linewidth = 1) +
  scale_fill_hue() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.2))) +
  labs(
    title = "Cancellation Rate - By Parking Lot",
    x     = "Parking Lot",
    y     = "Cancellation Rate (%)"
  ) +
  chart_theme +
  theme(
    legend.position    = "none",
    panel.grid.major.x = element_blank()
  )

ggsave("visualizations/cancellation_rate_by_lot.png", width = 12, height = 7,
       dpi = 300, bg = "white", device = ragg::agg_png)
```

:::{.alert .alert-warning}
**Watch Out:** `r cancellation_by_lot$car_park_name[1]` has the highest cancellation rate at `r round(cancellation_by_lot$cancel_rate[1], 2)`% (`r cancellation_by_lot$cancellations[1]` out of `r cancellation_by_lot$total_bookings[1]` bookings).
:::

## 4.3 Cancellation Reasons by Lot

```{r cancellation-reasons-by-lot}
cancellation_reasons <- data_clean %>%
  filter(!is.na(booking_cancellation_reason)) %>%
  group_by(car_park_name, booking_cancellation_reason) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(car_park_name) %>%
  mutate(
    total_lot_cancellations = sum(count),
    percentage = count / total_lot_cancellations * 100
  ) %>%
  arrange(car_park_name, desc(count))

top_reasons <- cancellation_reasons %>%
  group_by(car_park_name) %>%
  slice_max(order_by = count, n = 3) %>%
  ungroup()

kable(top_reasons %>%
        select(car_park_name, booking_cancellation_reason, count, percentage),
      digits = 1,
      col.names = c("Lot", "Cancellation Reason", "Count", "% of Lot Cancellations"),
      caption = "Top 3 Cancellation Reasons per Lot") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE) %>%
  pack_rows(index = table(top_reasons$car_park_name))
```

```{r cancellation-reasons-chart, fig.height=10}
if (nrow(cancellation_reasons) > 0) {
  ggplot(cancellation_reasons,
         aes(x = reorder(booking_cancellation_reason, count),
             y = count,
             fill = car_park_name)) +
    geom_col(alpha = 0.85, width = 0.7) +
    facet_wrap(~ car_park_name, ncol = 2, scales = "free") +
    coord_flip() +
    scale_fill_hue() +
    labs(
      title = "Cancellation Reasons - By Parking Lot",
      x     = "Cancellation Reason",
      y     = "Number of Cancellations"
    ) +
    chart_theme +
    theme(
      legend.position = "none",
      axis.text.x     = element_text(color = "#000000", size = 10, family = "sans"),
      axis.text.y     = element_text(color = "#000000", size = 10, family = "sans")
    )

  ggsave("visualizations/cancellation_reasons_by_lot.png", width = 12, height = 10,
         dpi = 300, bg = "white", device = ragg::agg_png)
}
```

---

## 4.4 Cancellation Timing by Lot

```{r prepare-cancellation-timing-data}
cancellation_by_dow_lot <- data_clean %>%
  mutate(
    booking_dow = wday(booking_date, label = TRUE, abbr = FALSE),
    booking_dow = factor(booking_dow,
                         levels = c("Monday", "Tuesday", "Wednesday", "Thursday",
                                    "Friday", "Saturday", "Sunday"))
  ) %>%
  group_by(car_park_name, booking_dow) %>%
  summarise(
    total_bookings = n(),
    cancellations  = sum(is_cancelled, na.rm = TRUE),
    cancel_rate    = mean(is_cancelled, na.rm = TRUE) * 100,
    .groups = "drop"
  )

plot_cancel_timing <- function(lot_name) {
  ggplot(cancellation_by_dow_lot %>% filter(car_park_name == lot_name),
         aes(x = booking_dow, y = cancel_rate, fill = booking_dow)) +
    geom_col(alpha = 0.85, width = 0.7) +
    geom_text(aes(label = sprintf("%.1f%%\n(%d/%d)",
                                  cancel_rate, cancellations, total_bookings)),
              vjust = -0.5, size = 3, color = "#000000", family = "sans") +
    scale_fill_hue() +
    scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
    labs(
      title = paste0("Cancellation Rate by Day of Week - ", lot_name),
      x     = "Day of Week",
      y     = "Cancellation Rate (%)"
    ) +
    chart_theme +
    theme(
      legend.position = "none",
      axis.text.x     = element_text(color = "#000000", size = 11,
                                     angle = 45, hjust = 1, family = "sans")
    )
}
```

### Lot 2 General

```{r cancellation-timing-lot2, fig.height=5}
plot_cancel_timing("Lot 2 General")
ggsave("visualizations/cancellation_timing_lot2.png", width = 10, height = 5,
       dpi = 300, bg = "white", device = ragg::agg_png)
```

### Lot 3

```{r cancellation-timing-lot3, fig.height=5}
plot_cancel_timing("Lot 3")
ggsave("visualizations/cancellation_timing_lot3.png", width = 10, height = 5,
       dpi = 300, bg = "white", device = ragg::agg_png)
```

### Lot 4 General

```{r cancellation-timing-lot4, fig.height=5}
plot_cancel_timing("Lot 4 General")
ggsave("visualizations/cancellation_timing_lot4.png", width = 10, height = 5,
       dpi = 300, bg = "white", device = ragg::agg_png)
```

### Lot 5

```{r cancellation-timing-lot5, fig.height=5}
plot_cancel_timing("Lot 5")
ggsave("visualizations/cancellation_timing_lot5.png", width = 10, height = 5,
       dpi = 300, bg = "white", device = ragg::agg_png)
```

### Lot 6

```{r cancellation-timing-lot6, fig.height=5}
plot_cancel_timing("Lot 6")
ggsave("visualizations/cancellation_timing_lot6.png", width = 10, height = 5,
       dpi = 300, bg = "white", device = ragg::agg_png)
```



---
